Use Of Jigsaw Puzzle Solving Algorithms In The Real World

### 2023-06-25 LaTeX_paper/paper.tex
backup commit
fix typo on paper
add section 6 and 6.1 to paper

\section{Previous Literature}
This section will analyze 3 different algorithms that have been proposed
as a solution of type 2 puzzles. The objective is to understand the
strengths and the weaknesses of each one, to build up some knowledge
that will be useful for the next section.

@@

\subsection{Comparing the sides}
The last step needed before it is possible to start working on
a solver algorithm, is to compare the sides that have been
generated by the previous step.\newline
In order to generate a compatibility shore,
the program compute the following steps:

@@

\begin{figure}[htbp]
  \centering
  \begin{minipage}[t]{0.44\textwidth}
    \vspace{3pt} % Ensure alignment of the top of the minipage
    \includegraphics[width=\textwidth]{pictures/side_comparation.png}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{0.54\textwidth}
    \caption{\newline
    In this image we can see two sides that have been
    compared, one side is drowned in red, the other one in blue.
    In this picture, the “Or Area” is represented by all non
    black pixels; The “And Area” is represented by all the
    purple pixels.}
  \end{minipage}
\end{figure}
\cleardoublepage

>>>>

\section{Previous Literature}
This section will analyze 3 different algorithms that have been proposed
as a solution of type 2 puzzles. The objective is to understand the
strengths and the weaknesses of each one, to build up some knowledge
that will be useful for the next sections.

@@

\subsection{Comparing the sides}\label{document:my_comparator}
The last step needed before it is possible to start working on
a solver algorithm, is to compare the sides that have been
generated by the previous step.\newline
In order to generate a compatibility shore,
the program compute the following steps:

@@

\begin{figure}[htbp]
  \centering
  \begin{minipage}[t]{0.44\textwidth}
    \vspace{3pt} % Ensure alignment of the top of the minipage
    \includegraphics[width=\textwidth]{pictures/side_comparation.png}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{0.54\textwidth}
    \caption{\newline
    In this image we can see two sides that have been
    compared, one side is drowned in red, the other one in blue.
    In this picture, the “Or Area” is represented by all non
    black pixels; The “And Area” is represented by all the
    purple pixels.}
  \end{minipage}
\end{figure}
\clearpage

\section{Apling already existing algorithm to the real world}
Now that the setup is completed, it is possible to test the already existing
algorithms with real world puzzles, to see if they can work. For this test,
the fist algorithm~\ref{document:GCL} has been chosen, because the paper is full of detail.
In particular it had some information about the accuracy of the algorithm in
function to the corruption rate, which are essential for this analysis.
\newline \newline
The tests that have been conducted have shown that our comparator algorithm~\ref{document:my_comparator}
and the “Graph Connection Laplacian” solution~\ref{document:GCL} are not compatible with each other.
A proof for this claim follows.

\subsection{Proof}

This section will provide a proof for the incompatibility of
the two algorithms mentioned above.
\newline \newline
The comparison algorithm deceived in section~\ref{document:my_comparator} outputs a compatibility
shore that goes from 0 to 1.\newline
But the algorithm~\ref{document:GCL} takes as input a binary value,
which means that it is necessary to apply a threshold to the input
data to convert them from float to bool.
\newline \newline
To find the optimal threshold a small 16 piece puzzle has been solved.
And the following 4 values have been measured, in function of the threshold:

\begin{itemize}
  \item \textbf{match\%:}\newline
  The probability that 2 random sides match.

  \item \textbf{correct combination match\% (or c.c match\%):}\newline
  The probability that 2 sides match given that in the correct puzzle
  solution they actually are close to each other. ideally this should be 1.

  \item \textbf{limit match\%:}\newline
  Given that this measure has been taken on a 16 piece puzzle,
  the match\% is highly influenced by the correct piece matching.
  With a bigger puzzle the match\% would be lower.
  Limit match\% is an approximation of what the match\%
  would be in the limit for \(N \rightarrow + \infty\) (where N is the number of pieces).
  This value is obtained by subtracting to match\%
  the probability of choosing randomly the correct side,
  multiplied by the probability that the comparison returns true
  (which is c.c match\%). ideally this should be almost zero.
  \[limit \: math\% = math\% - \frac{c.c. \: mathc\%}{16 \times 4}\]

  \item \textbf{corruption rate:}\newline
\end{itemize}
